### 2024-03-27 paper/paper.qmd
change

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Yichen ji
thanks: "Code and data are available at: https://github.com/Selinayichenji/Canadian_election_prediction.git."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-03-27 scripts/00-simulate_data.R

@@ -1,0 +1,15 @@
+#### Preamble ####
+# Purpose: Simulate data for election survey
+# Author: Yichen Ji
+# Date: 09 March 2024
+# Contact: yic.ji@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: Download tidyverse package
+# Any other information needed? No.
+
+#### Workspace setup ####
+library(tidyverse)
+# [...UPDATE THIS...]
+
+#### Simulate data ####
+# [...ADD CODE HERE...]

### 2024-03-27 scripts/01-download_data.R

@@ -1,0 +1,20 @@
+#### Preamble ####
+# Purpose: Downloads and saves the data from Harvard Dataverse
+# Author: Yichen Ji
+# Date: 09 March 2024
+# Contact: yic.ji@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: downloading the packages "rvest" and "httr"
+# Any other information needed? No.
+
+
+#### Workspace setup ####
+library(rvest)
+library(httr)
+
+#### Download data ####
+download_url_survey <- "https://dataverse.harvard.edu/api/access/datafile/7517836"
+destifile_survey <- "data/raw_data/2021survey.tab"
+GET(download_url_survey,write_disk(destifile_survey,overwrite = TRUE))
+
+

### 2024-03-27 scripts/02-data_cleaning.R

@@ -1,0 +1,72 @@
+#### Preamble ####
+# Purpose: Transform data from tab file into parquet file and filter esstential columns and individuals
+# Author: Yichen Ji
+# Date: 09 March 2024
+# Contact: yic.ji@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: Download tidyverse package
+# Any other information needed? No.
+
+#### Workspace setup ####
+library(tidyverse)
+library(arrow)
+
+#### Clean data ####
+survey_data <- read.delim("data/raw_data/2021survey.tab")
+
+survey_data <- 
+  survey_data %>% 
+  mutate(age = case_when(cps21_age >= 18 & cps21_age <= 29 ~ "18-29",
+                         cps21_age >= 30 & cps21_age <= 44 ~ "30-44",
+                         cps21_age >= 45 & cps21_age <= 59 ~ "45-59",
+                         cps21_age>= 60 & cps21_age <= 74 ~ "60-74",
+                         cps21_age > 74 ~ "75+"),
+         vote_liberal = ifelse(cps21_votechoice==1, 1, 0),
+         vote_conservative = ifelse(cps21_votechoice==2, 1, 0),
+         vote_NDP = ifelse(cps21_votechoice == 3, 1, 0),
+         gender = case_when(cps21_genderid == 1 ~ "Male",
+                            cps21_genderid == 2 ~ "Female"), 
+         education_level = case_when(cps21_education %in% c(1,2,3,4) ~ "Less than high school", 
+                                     #Less than high school diploma or its equivalent
+                                     cps21_education %in% c(5,6)  ~ "High school",
+                                     #High school diploma or a high school equivalency certificate
+                                     cps21_education == 7 ~ "Non-University", 
+                                     #Completed technical, community college, CEGEP, College Classique
+                                     cps21_education == 8 ~ "University certificate below the bachelor", 
+                                     #University certificate or diploma below the bachelor's level
+                                     cps21_education == 9 ~ "Bachelor's degree", 
+                                     cps21_education %in% c(10,11) ~ "Above the bachelor"),
+         # University certificate, diploma or degree above the bachelor
+         family_income = cut(cps21_income_number, breaks = c(0, 24999, 49999, 74999, 99999, 124999, Inf), 
+                             labels = c("Less than $25,000", "$25,000 to $49,999", "$50,000 to $74,999", "$75,000 to $99,999",
[…]

### 2024-03-27 scripts/03-test_data.R

@@ -1,0 +1,15 @@
+#### Preamble ####
+# Purpose: Test data
+# Author: Yichen Ji
+# Date: 27 March 2024
+# Contact: yic.ji@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: none
+# Any other information needed? No.
+
+#### Workspace setup ####
+library(arrow)
+
+analysis_data <- read_parquet("data/analysis_data/analysis_data.parquet")
+
+#### Test data ####

### 2024-03-27 scripts/04-model.R

@@ -1,0 +1,36 @@
+#### Preamble ####
+# Purpose: Models for predicting 2024 Canadian election
+# Author: Yichen Ji
+# Date: 27 March 2024
+# Contact: yic.ji@mail.utoronto.ca
+# License: MIT
+# Pre-requisites:
+# Any other information needed? None
+
+
+
+#### Workspace setup ####
+library(tidyverse)
+library(rstanarm)
+
+#### Read data ####
+analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+
+### Model data ####
+first_model <-
+  stan_glm(
+    formula = flying_time ~ length + width,
+    data = analysis_data,
+    family = gaussian(),
+    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    prior_aux = exponential(rate = 1, autoscale = TRUE),
+    seed = 853
+  )
+
+
+#### Save model ####
+saveRDS(
+  first_model,
+  file = "models/first_model.rds"
+)

### 2024-04-02 paper/paper.qmd
update

@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "1) what was done, 2) what was found, and 3) why this matters (all at a high level). ."
 format: pdf
@@
 
-You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.
+This report utilizes the 2021 Canadian Election Study data and the "General Social Survey, Cycle 31: Families, Public Use Microdata File Documentation and User's Guide" (Statistics Canada, 2019) to solve the emergent dilemma of diminishing vote participation rate.
+The primary purpose of this report is to use the data set to predict future voter turnout by differentiating throughout the province(note: not include Quebec, Yukon, Northwest Territories, and Nunavut).
 
-The remainder of this paper is structured as follows. @sec-data....
+Based on previous voting analysis, the main factors affecting voting include age, education level, family status(represented by the number of children), and economic well-being(represented by the family income).
+("Factors Associated with Voting," 2015) Thus, the examination will focus on demographic variables, including age, gender, family income, education level, and the number of children in the vote rate corresponding to Canada's three main political parties.
+The three main political parties are Liberal, Conservative, and NDP(Canada's New Democrats), which occupied around 90 percent of the election 2010s.
+("Canadian Federal Election Results," n.d.) The report will use logistic regression on different parties to model the participation rate.
+Whether the voting for particular parties or not will be recorded binary, as 1 or 0.
+Under this method, we assume the authenticity of our source, 2021 Canadian Election Study data, to build up the model.
+
+The importance of this study is to reveal the complexities behind the recent decline in voter participation rates.
+By exploring the complex demographic factors and the voting rate of different political parties, this report could provide insights into the advantages of each of the three main parties during the election.
+According to past data, where liberals always take up the majority of the voting, we will assume the liberals will win the overall election.
+(Simon Fraser University, n.d.) Meanwhile, this report will examine how various demographic elements correlate with political affiliations, aiming to understand the challenges facing Canadian democracy comprehensively.
+In addition, the findings can not only predict the democratic participation rate throughout different states but also serve as a potential solution to the diminishing voting participation rate corresponding to each province, which can strengthen democracy throughout the nation.
+
+## estimand
+
+ The paper introduces the basic information contains data source, methodology, variables and measurements in @sec-data.
+The visualization and analysis of the tendency differences in moderation by people across three social factors are presented in @sec-result.
+And in @sec-dis, we discuss what we have learned, our understanding of the world, the limitations, and the next steps of our research.
+@sec-app is for appendix and @sec-ref is listed all references in this paper.
 
@@
 
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+The survey data was sourced from the "2021 Canadian Election Study" (Stephenson, Harell, Rubenson, & Loewen, 2022), and the census information was obtained from the "General Social Survey, Cycle 31: Families, Public Use Microdata File Documentation and User’s Guide" (Statistics Canada, 2019).
 
-```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
-#| echo: false
+## Analysis Tools
+Our paper applies using the statistical programming language R [@citeR].
+Besides the programming tool, we also employ the following packages: readr [@read], ggplot2 [@gg2], dplyr [@dpr], tidyverse [@tidy], MetBrewer [@met], knitr [@citeknr], tidyr[@tdr], kableExtra[@kbe] and grid[@grid].
 
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
-```
+## Variables
 
-Talk more about it.
+>**Age**: include five different groups: 18-29 years old, 30-44 years old, 45-59 years old, 60-74 years old, and above 74 years old.
+We manipulate the age for census data, which has different years than the survey data.
 
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
+>**vote_liberal/vote_conservative/vote_NDP**: the voting result on whether to vote for three different parties. (Liberal, Conservative, or NDP) The result of voting or not is recorded in binary.
 
-```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
-#| echo: false
-#| warning: false
-#| message: false
+>**Gender**: only include two types of gender, female and male, excluding non-binary or others
 
-analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
+>**education_level**: including six different education levels(Less than high school, High school, Non-University, University certificate below the bachelor, Bachelor's degree, Above the bachelor).
 
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
-```
+>**family_income**: including six different groups. ("Less than 25,000", "25,000 to 49,999", "50,000 to 74,999", "75,000 to 99,999", "100,000 to 124,999", "125,000 and more")
 
-Talk way more about it.
+>**Province**: 9 different states and excluding Quebec, Yukon, Northwest Territories, and Nunavut.
+
+>**children_number**: the number of children within the family, which includes only six levels (0,1,2,3,4 and 4+ children)
+
+## Measurement
+The CES 2021, consisting of an online cohort of 20,968 participants from the broader Canadian populace, was facilitated via the Leger Opinion panel.
+This study was structured in two distinct stages: the campaign period survey (CPS) and the post-election survey (PES).
+The CPS phase was further divided into three segments – "CPS", "CPS Modules", and "CPS Oversample", which were later consolidated into one dataset.
+Regarding the PES, all individuals who participated in the CPS were invited back for this subsequent survey after the election.
+Out of these, 15,069 individuals completed the PES, marking a response rate of 72%.
+
+## Survey data summary
+
+distribution of age, gender, income, education level, province, children number
 
@@
 
-## Model set-up
-
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+## Multilevel Logistic Regression Model
 
 \begin{align}
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
+y_i | \pi_i &\sim \text{Bern}(\pi_i) \\
+\text{logit}(\pi_i) &= \beta_0 + \alpha_{g[i]}^{\text{age}}+ \alpha_{g[i]}^{\text{gender}} + \alpha_{s[i]}^{\text{education level}} 
++\alpha_{s[i]}^{\text{family income}} + \alpha_{s[i]}^{\text{children number}} + \alpha_{s[i]}^{\text{state}} \\
+\beta_0 &\sim \text{Normal}(0, 2.5) \\
+\alpha_{g}^{\text{age}} &\sim \text{Normal}(0, 2.5) \text{ for } g = 1,2,3,4,5 \\
+\alpha_{g}^{\text{gender}} &\sim \text{Normal}(0, 2.5) \text{ for } g = 1,2 \\
+\alpha_{g}^{\text{education level}} &\sim \text{Normal}(0, 2.5) \text{ for } g = 1,2,3,4,5,6 \\
+\alpha_{g}^{\text{family income}} &\sim \text{Normal}(0, 2.5) \text{ for } g = 1,2,3,4,5,6 \\
+\alpha_{g}^{\text{children number}} &\sim \text{Normal}(0, 2.5) \text{ for } g = 1,2,...,6 \\
+\alpha_{s}^{\text{state}} &\sim \text{Normal}(0, \sigma_{\text{state}}^2) \text{ for } s = 1,2,...,9 \\
+\sigma_{\text{state}} &\sim \text{Exponential}(1)
 \end{align}
@@
 We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+
+$$ log(\frac{p_{ij}}{1-p_{ij}}) = \beta_{0j}+\beta_1  x_{ij\ age} + \beta_2 x_{ij\ gender} + \beta_3  x_{ij\ education\ level} + \beta_4  x_{ij\ family\ income} + \beta_5  x_{ij\ children\ number}$$
+
+$$\beta_{0j} \thicksim Normal(\mu_{\beta_{0}}, \sigma^2_{\beta_{0}})$$
+
+In the model, $j$ is the province and $i$ is the individual voter indicator.
+
+$p$ represents the probability of the event of interest occurring,
+which is the voter's probability of voting for any specific party. $p_{ij}$
+means the voting of any specific party probability of ith voter in jth
+province.\
+
+$log(\frac{p_{ij}}{1-p_{ij}})$ means the log of odds of voting for
+ any specific party.\
+
+$\beta_0$ represents the intercept of the model and is the log of odds
+of voting for any specific party when the individual is at a certain age,
+with a certain gender, education level, family income and children
+number.\
+
+$\beta_{0j}$ stands for jth province effect on the log of odds of voting for
+any specific party, and we assume the intercept $\beta_{0j}$ in different
+provinces is random and follows a normal distribution with mean
+$\mu_{\beta_{0}}$ and variance $\sigma^2_{\beta_{0}}$.\
+
+$\beta_1$ represents the slope of age level in the model, then for any voter,
+one unit increase in age, we expect a $\beta_1$ increase in log odds of
+voting for any specific party. $\beta_2$ represents the average difference in
+log odds of voting for any specific party between Males and Females for a
+certain age, education level, family income and children number.\
+
+$\beta_3$ represents the average difference in log odds of voting for
+any specific party between groups with different education levels for a
+certain age, gender, family income and children number.\
+
+$\beta_4$ represents the average difference in log odds of voting for
+any specific party between groups with different family income levels for a certain
+age, gender, education level and children number.\
+
+$\beta_5$ represents the average difference in log odds of voting for
+any specific party between groups with different children number levels for a
+certain age, gender, education level and family income.\
+
+$x_{ij}$ is a binary variable, it can only be 1 or 0 as all the variables we have are categorical, it also stands for the ith voter in jth province.
 
@@
 
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-
-library(rstanarm)
-
-first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
-
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
-)
-```
-
 # Discussion
+What is done in this paper?
+What is something that we learn about the world?
+What is another thing that we learn about the world?
+What are some weaknesses of what was done?
+What is left to learn or how should we proceed in the future?
 
@@
 
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
-
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
-
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
-```
-
 ## Diagnostics
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
-
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
-
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
-```
 

### 2024-04-02 scripts/04-model.R

@@ -7,27 +7,66 @@
 # Pre-requisites:
 # Any other information needed? None
 
-
-
 #### Workspace setup ####
 library(tidyverse)
 library(rstanarm)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+analysis_data <- read_csv("data/analysis_data/analysis_data.parquet")
 
 ### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
 
+liberal_model <- stan_glmer(
+  vote_liberal ~ age + gender + education_level + family_income + children_number + (1 | province),
+  data = data,
+  family = binomial(link = "logit"),
+  prior = normal(0, 2.5, autoscale = TRUE), 
+  prior_intercept = normal(0, 2.5, autoscale = TRUE), 
+  seed = 2024,
+  chains = 4,
+  cores = 4,
+  control = list(adapt_delta = 0.99)
+)
+
+saveRDS(
+  liberal_model,
+  file = "liberal.rds"
+)
+
+
+conservative_model <- stan_glmer(
+  vote_conservative ~ age + gender + education_level + family_income + children_number + (1 | province),
+  data = data,
+  family = binomial(link = "logit"),
+  prior = normal(0, 2.5, autoscale = TRUE), 
+  prior_intercept = normal(0, 2.5, autoscale = TRUE), 
+  seed = 2024,
+  chains = 4,
+  cores = 4,
+  control = list(adapt_delta = 0.99)
+)
+
+saveRDS(
+  conservative_model,
+  file = "liberal.rds"
+)
+
+
+NDP_model <- stan_glmer(
+  vote_NDP ~ age + gender + education_level + family_income + children_number + (1 | province),
+  data = data,
+  family = binomial(link = "logit"),
+  prior = normal(0, 2.5, autoscale = TRUE), 
+  prior_intercept = normal(0, 2.5, autoscale = TRUE), 
+  seed = 2024,
+  chains = 4,
+  cores = 4,
+  control = list(adapt_delta = 0.99)
+)
+saveRDS(
[…]

### 2024-04-02 scripts/04-model.R
update

@@ -12,13 +12,15 @@ library(tidyverse)
 library(rstanarm)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.parquet")
+library(arrow)
+
+analysis_data <- read_parquet("data/analysis_data/analysis_data.parquet")
 
 ### Model data ####
 
 liberal_model <- stan_glmer(
   vote_liberal ~ age + gender + education_level + family_income + children_number + (1 | province),
-  data = data,
+  data = analysis_data,
   family = binomial(link = "logit"),
   prior = normal(0, 2.5, autoscale = TRUE), 
   prior_intercept = normal(0, 2.5, autoscale = TRUE), 
@@ -28,15 +30,13 @@ liberal_model <- stan_glmer(
   control = list(adapt_delta = 0.99)
 )
 
-saveRDS(
-  liberal_model,
-  file = "liberal.rds"
-)
+summary(liberal_model)
 
+saveRDS(liberal_model, file = "models/liberal_model.rds")
 
 conservative_model <- stan_glmer(
   vote_conservative ~ age + gender + education_level + family_income + children_number + (1 | province),
-  data = data,
+  data = analysis_data,
   family = binomial(link = "logit"),
   prior = normal(0, 2.5, autoscale = TRUE), 
   prior_intercept = normal(0, 2.5, autoscale = TRUE), 
@@ -45,16 +45,13 @@ conservative_model <- stan_glmer(
   cores = 4,
   control = list(adapt_delta = 0.99)
 )
-
-saveRDS(
-  conservative_model,
-  file = "liberal.rds"
-)
+summary(conservative_model)
+saveRDS(conservative_model, file = "models/conservative_model.rds")
 
 
 NDP_model <- stan_glmer(
   vote_NDP ~ age + gender + education_level + family_income + children_number + (1 | province),
-  data = data,
+  data = analysis_data,
   family = binomial(link = "logit"),
   prior = normal(0, 2.5, autoscale = TRUE), 
   prior_intercept = normal(0, 2.5, autoscale = TRUE), 
@@ -63,13 +60,5 @@ NDP_model <- stan_glmer(
   cores = 4,
   control = list(adapt_delta = 0.99)
 )
-saveRDS(
-  NDP_model,
-  file = "liberal.rds"
-)
-
-#### Save model ####
-saveRDS(
-  first_model,
-  file = "models/first_model.rds"
-)
+summary(NDP_model)
+saveRDS(NDP_model, file = "models/NDP_model.rds")

### 2024-04-02 paper/paper.qmd
update

@@
 
-```{r}
+```{r setup}
 #| include: false
@@
 library(tidyverse)
-library(palmerpenguins)
+library(arrow)
+```
+
+```{r}
+#| label: cleaned
+#| warning: false
+#| message: false
+#| results: 'hide'
+#| echo: false
+
+analysis_data <- read_parquet("data/analysis_data/analysis_data.parquet")
+
 ```
@@
 
+## Sample of cleaned data
+
 ## Measurement
@@
 y_i | \pi_i &\sim \text{Bern}(\pi_i) \\
-\text{logit}(\pi_i) &= \beta_0 + \alpha_{g[i]}^{\text{age}}+ \alpha_{g[i]}^{\text{gender}} + \alpha_{s[i]}^{\text{education level}} 
-+\alpha_{s[i]}^{\text{family income}} + \alpha_{s[i]}^{\text{children number}} + \alpha_{s[i]}^{\text{state}} \\
+\text{logit}(\pi_i) &= \beta_0 + \alpha_{a[i]}^{\text{age}}+ \alpha_{g[i]}^{\text{gender}} + \alpha_{e[i]}^{\text{education level}} 
++\alpha_{f[i]}^{\text{family income}} + \alpha_{c[i]}^{\text{children number}} + \alpha_{s[i]}^{\text{state}} \\
 \beta_0 &\sim \text{Normal}(0, 2.5) \\
-\alpha_{g}^{\text{age}} &\sim \text{Normal}(0, 2.5) \text{ for } g = 1,2,3,4,5 \\
+\alpha_{a}^{\text{age}} &\sim \text{Normal}(0, 2.5) \text{ for } g = 1,2,3,4,5 \\
 \alpha_{g}^{\text{gender}} &\sim \text{Normal}(0, 2.5) \text{ for } g = 1,2 \\
-\alpha_{g}^{\text{education level}} &\sim \text{Normal}(0, 2.5) \text{ for } g = 1,2,3,4,5,6 \\
-\alpha_{g}^{\text{family income}} &\sim \text{Normal}(0, 2.5) \text{ for } g = 1,2,3,4,5,6 \\
-\alpha_{g}^{\text{children number}} &\sim \text{Normal}(0, 2.5) \text{ for } g = 1,2,...,6 \\
+\alpha_{e}^{\text{education level}} &\sim \text{Normal}(0, 2.5) \text{ for } g = 1,2,3,4,5,6 \\
+\alpha_{f}^{\text{family income}} &\sim \text{Normal}(0, 2.5) \text{ for } g = 1,2,3,4,5,6 \\
+\alpha_{c}^{\text{children number}} &\sim \text{Normal}(0, 2.5) \text{ for } g = 1,2,...,6 \\
 \alpha_{s}^{\text{state}} &\sim \text{Normal}(0, \sigma_{\text{state}}^2) \text{ for } s = 1,2,...,9 \\
@@
 
-Our results are summarized in @tbl-modelresults.
+```{r echo=FALSE}
+# Retrieve the Bayesian linear model from the saved .rds file
+liberal_model <- readRDS(file = "models/liberal_model.rds")
+
+```
 

### 2024-04-02 scripts/00-simulate_data.R

@@ -9,7 +9,5 @@
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
 
 #### Simulate data ####
-# [...ADD CODE HERE...]

### 2024-04-02 scripts/03-test_data.R

@@ -9,7 +9,30 @@
 
 #### Workspace setup ####
 library(arrow)
-
+library(testthat)
 analysis_data <- read_parquet("data/analysis_data/analysis_data.parquet")
 
 #### Test data ####
+
+#test gender and age group
+expect_setequal(unique(analysis_data$gender), c("Female", "Male"))
+
+
+expect_setequal(unique(analysis_data$age), c("18-29", "30-44", "45-59", "60-74", "75+"))
+
+
+#test binomial result of vote
+expect_true(all(analysis_data$vote_liberal %in% c(0, 1)))
+
+expect_true(all(analysis_data$vote_conservative %in% c(0, 1)))
+
+expect_true(all(analysis_data$vote_NDP %in% c(0, 1)))
+
+
+#test provinces
+expected_provinces <- c("British Columbia", "Ontario", "Manitoba", "Alberta",
+                        "New Brunswick", "Newfoundland and Labrador",
+                        "Nova Scotia", "Prince Edward Island", "Saskatchewan")
+
+expect_setequal(unique(analysis_data$province), expected_provinces)
+

### 2024-04-02 paper/paper.qmd
update

@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "Analysising social factors influence Canadian voters' choices"
+subtitle: "Decoding CES 2021 Vote Data by using A Multilevel Logistic Regression Model"
 author: 
@@
 format: pdf
+toc: true
 number-sections: true
 bibliography: references.bib
+link-citations: true
 ---
@@
 #| message: false
+library(tidyverse)
 
-library(tidyverse)
+library(here)
+library(dplyr)
 library(arrow)
+library(ggplot2)
+library(kableExtra)
+library(bayesplot)
+library(rstanarm)
+
 ```
 
-```{r}
-#| label: cleaned
-#| warning: false
-#| message: false
-#| results: 'hide'
-#| echo: false
-
-analysis_data <- read_parquet("data/analysis_data/analysis_data.parquet")
-
+```{r include=FALSE, message=FALSE}
+# read the data file and store it in the 'data' variable
+analysis_data <- read_parquet(here("data", "analysis_data", "analysis_data.parquet"))
 ```
@@
 
-The survey data was sourced from the "2021 Canadian Election Study" (Stephenson, Harell, Rubenson, & Loewen, 2022), and the census information was obtained from the "General Social Survey, Cycle 31: Families, Public Use Microdata File Documentation and User’s Guide" (Statistics Canada, 2019).
+The survey data was sourced from the "2021 Canadian Election Study" (Stephenson, Harell, Rubenson, & Loewen, 2022).
 
@@
 
+\newpage
 ## Sample of cleaned data
+
+```{r}
+#| label: tbl-cleaned
+#| tbl-cap: Sample of the Cleaned Data
+#| warning: false
+#| echo: false
+
+head(analysis_data, 5) |>
+  kable(
+    col.names = c("age", "vote_liberal", "vote_conservative", "vote_NDP","gender","education_level","family_income","province","children_number"),
+    booktabs = TRUE
+  )
+
+```
+
+## Survey data summary
+
+All detailed tables include summary data of 6 variables are in @sec-A
+age, gender, income, education level, province, children number
+
+```{r}
+#| label: fig-pro
+#| fig-cap:  Population Distribution by Province in CES2021
+#| warning: false
+#| echo: false
+
+province_plot <- analysis_data %>%
+  count(province) %>%
+  mutate(percentage = n / sum(n) * 100)
+
+ggplot(province_plot, aes(x = province, y = percentage, fill = province)) +
+  geom_bar(stat = "identity",fill = "navyblue") +
+  labs(x = "Province", y = "Percentage of Total") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
+```
+
+```{r}
+library(dplyr)
+library(ggplot2)
+
+# Define a function to calculate percentages for each category within a variable
+calculate_percentage <- function(data, category) {
+  data %>%
+    count(!!sym(category)) %>%
+    mutate(percentage = n / sum(n) * 100) %>%
+    rename(Category = !!sym(category)) %>%
+    mutate(Variable = category)  # store the variable name
+}
+
+# Apply the function to each of the variables you are interested in
+category_list = c("age", "gender", "family_income", "education_level", "province", "children_number")
+percentages <- lapply(category_list, calculate_percentage, data = analysis_data)
+
+# Combine the list of data frames into one data frame
+percentages_df <- bind_rows(percentages)
+
+# Generate the plot
+combined_plot <- ggplot(percentages_df, aes(x = Category, y = percentage, fill = Variable)) +
+  geom_bar(stat = "identity") +
+  facet_wrap(~Variable, scales = "free_x") + # allows each facet to have its own x axis
+  labs(x = "Category", y = "Percentage of Total") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  scale_fill_brewer(palette = "Set1")
+
+# Print the combined plot
+combined_plot
+
+```
 
@@
 Out of these, 15,069 individuals completed the PES, marking a response rate of 72%.
+Respondents needed to be aged 18 or over and Canadian citizens or permanent residents in order to participate.
 
-## Survey data summary
-
-distribution of age, gender, income, education level, province, children number
-
-# Model
+# Model {#sec-models}
 
@@
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+We run the model in R using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+The `stan_glm` function from `rstanarm`
+
+### Model justification
+
+We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+
+We can use maths by including latex between dollar signs, for instance $\theta$.
 
@@
 
-### Model justification
+# Results {#sec-result}
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+```{r}
+#| label: models
+#| warning: false
+#| message: false
+#| echo: false
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
+liberal_model <- readRDS("../models/liberal_model.rds")
+cons_model <- readRDS("../models/conservative_model.rds")
+NDP_model <- readRDS("../models/NDP_model.rds")
+```
 
-# Results
+## Model Coefficients
 
-```{r echo=FALSE}
-# Retrieve the Bayesian linear model from the saved .rds file
-liberal_model <- readRDS(file = "models/liberal_model.rds")
+```{r}
+#| label: tbl-liberal
+#| tbl-cap: Coefficients of social factors influence vote for liberal party
+#| warning: false
+#| echo: false
+library(modelsummary)
+
+modelsummary(
+  list(
+    "Vote for Liberal Party" = liberal_model 
+  ),
+  statistic = "mad", 
+  booktabs = TRUE 
+)
 
@@
 
-# Discussion
+# Discussion {#sec-dis}
 What is done in this paper?
@@
 
-# Appendix {-}
+# Appendix {#sec-A}
 
@@
 
-## Posterior predictive check
+## Posterior predictive check {#sec-posterior}
+
+```{r fig-posterior-plot, echo=FALSE, fig.cap="pp check"}
+
+pp_check(liberal_model) + 
+  theme_classic() +
+  theme(legend.position = "bottom")
+
+pp_check(cons_model) + 
+  theme_classic() +
+  theme(legend.position = "bottom")
+
+pp_check(NDP_model) + 
+  theme_classic() +
+  theme(legend.position = "bottom")
+```
 

### 2024-04-02 scripts/00-simulate_data.R

@@ -11,3 +11,14 @@
 library(tidyverse)
 
 #### Simulate data ####
+set.seed(853)
+
+liberal_support <-
+  tibble(
+    state = sample(1:50, size = 1000, replace = TRUE),
+    gender = sample(c(1, 2), size = 1000, replace = TRUE),
+    noise = rnorm(n = 1000, mean = 0, sd = 10) |> round(),
+    supports = if_else(state + gender + noise > 50, 1, 0)
+  )
+
+political_support

### 2024-04-02 paper/paper.qmd
update

@@
 library(rstanarm)
+library(tidyr)
 
@@
 And in @sec-dis, we discuss what we have learned, our understanding of the world, the limitations, and the next steps of our research.
-@sec-app is for appendix and @sec-ref is listed all references in this paper.
+@sec-A is for appendix and @sec-ref is listed all references in this paper.
 
@@
     booktabs = TRUE
-  )
+  )%>%
+  kable_styling(latex_options = c("scale_down"))
 
@@
 
-```{r}
-#| label: fig-pro
-#| fig-cap:  Population Distribution by Province in CES2021
+```{r, fig.width=10, fig.height=6}
+#| echo: false
+#| eval: true
+#| label: fig-percent
+#| fig-cap: Percentage of different groups in a category
 #| warning: false
-#| echo: false
 
-province_plot <- analysis_data %>%
-  count(province) %>%
-  mutate(percentage = n / sum(n) * 100)
+analysis_data_2 <- analysis_data
+labels_province <- c("Ontario" = "ON", "Quebec" = "QC", "British Columbia" = "BC", "Alberta" = "AB",
+                     "Manitoba" = "MB", "New Brunswick" = "NB", "Newfoundland and Labrador" = "NL",
+                     "Nova Scotia" = "NS", "Prince Edward Island" = "PE", "Saskatchewan" = "SK")
 
-ggplot(province_plot, aes(x = province, y = percentage, fill = province)) +
-  geom_bar(stat = "identity",fill = "navyblue") +
-  labs(x = "Province", y = "Percentage of Total") +
-  theme_minimal() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
-```
+analysis_data_2 <- analysis_data_2 %>%
+  mutate(province = recode(province, !!!labels_province))
 
-```{r}
-library(dplyr)
-library(ggplot2)
+#origin<-c("Less than $25,000", "$25,000 to $49,999", "$50,000 to $74,999", "$75,000 to $99,999",
+                                     #   "$100,000 to $124,999", "$125,000 and more")
+
+labels_income <- c("Less than $25,000" = "<25k", "$25,000 to $49,999"= "25~50k","$50,000 to $74,999" = "50~75k","$75,000 to $99,999" = "75~100k","$100,000 to $124,999" = "100~125k","$125,000 and more" = ">125k")
+analysis_data_2 <- analysis_data_2 %>%
+  mutate(family_income = recode(family_income, !!!labels_income))
+
+labels_education <- c(
+  "Less than high school" = "Below HS",
+  "High school" = "HS Grad",
+  "Non-University" = "Non-Uni",
+  "University certificate below the bachelor" = "Uni Cert",
+  "Bachelor's degree" = "Bachelor",
+  "Above the bachelor" = "Post-Bach"
+)
+
+analysis_data_2 <- analysis_data_2 %>%
+  mutate(education_level = recode(education_level, !!!labels_education))
 
@@
 category_list = c("age", "gender", "family_income", "education_level", "province", "children_number")
-percentages <- lapply(category_list, calculate_percentage, data = analysis_data)
+percentages <- lapply(category_list, calculate_percentage, data = analysis_data_2)
 
@@
 percentages_df <- bind_rows(percentages)
+
+income_levels_order <- c("<25k","25~50k","50~75k","75~100k","100~125k",">125k")
+percentages_df <- percentages_df %>%
+  mutate(Category = if_else(Variable == "family_income", factor(Category, levels = income_levels_order), as.factor(Category)))
+
+educ_levels_order <- c("Below HS","HS Grad", "Non-Uni","Uni Cert","Bachelor","Post-Bach")
+percentages_df <- percentages_df %>%
+  mutate(Category = if_else(Variable == "education_level", factor(Category, levels = educ_levels_order), as.factor(Category)))
 
@@
   facet_wrap(~Variable, scales = "free_x") + # allows each facet to have its own x axis
-  labs(x = "Category", y = "Percentage of Total") +
+  labs( y = "Percentage of Total") +
   theme_minimal() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  theme(axis.text.x = element_text(angle = 25, hjust = 1)) +
   scale_fill_brewer(palette = "Set1")
@@
 combined_plot
+
+```
+
+```{r, fig.width=10, fig.height=6}
+#| echo: false
+#| eval: true
+#| label: fig-vote-percent
+#| fig-cap: Percentage of Voting for 3 parties in different groups
+#| warning: false
+survey_long <- analysis_data_2 %>%
+  pivot_longer(cols = starts_with("vote_"), 
+               names_to = "party", 
+               values_to = "vote") %>%
+  pivot_longer(cols = c("age", "gender", "family_income", "education_level", "province", "children_number"),
+               names_to = "category",
+               values_to = "group") %>%
+  group_by(category, group, party) %>%
+  summarise(vote_percent = mean(vote, na.rm = TRUE), .groups = 'drop') %>%
+  ungroup()
+
+survey_long <- survey_long %>%
+  mutate(group = case_when(
+    category == "family_income" & group %in% c("<25k","25~50k","50~75k","75~100k","100~125k",">125k") ~ factor(group, levels = c("<25k","25~50k","50~75k","75~100k","100~125k",">125k")),
+    category == "education_level" & group %in% c("Below HS","HS Grad", "Non-Uni","Uni Cert","Bachelor","Post-Bach") ~ factor(group, levels = c("Below HS","HS Grad", "Non-Uni","Uni Cert","Bachelor","Post-Bach")),
+    TRUE ~ as.factor(group)
+  ))
+
+ggplot(survey_long, aes(x = group, y = vote_percent, color = party, group = party)) +
+  geom_line() + 
+  geom_point() + 
+  scale_color_manual(values = c("vote_liberal" = "red", 
+                                "vote_conservative" = "blue", 
+                                "vote_NDP" = "orange")) +
+  labs(title = "Voting Preferences by Category in Survey",
+       x = "Group", 
+       y = "Percentage", 
+       color = "Party") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 25, hjust = 1)) +
+  facet_wrap(~category, scales = "free_x", ncol = 2)
 
@@
 #| echo: false
+
 library(modelsummary)
-
-modelsummary(
-  list(
-    "Vote for Liberal Party" = liberal_model 
-  ),
+library(kableExtra)
+# 首先获取模型摘要
+msummary <- modelsummary(
+  list("Vote for Liberal Party" = liberal_model),
   statistic = "mad",
@@
 
+# 然后我们将msummary的结果分为两部分
+# 以下是一个如何操作的例子
+# 请注意，这需要您手动指定分割点
+# 比如，假设我们有10个系数，我们可以在第5个系数处分割
+part1 <- msummary[1:11,]
+part2 <- msummary[11:22,]
+
+# 创建两个并排的表格
+table1 <- kable(part1, booktabs = TRUE) %>%
+  kable_styling(font_size = 7) %>%
+  pack_rows(index = c("Part 1"))
+
+table2 <- kable(part2, booktabs = TRUE) %>%
+  kable_styling(font_size = 7) %>%
+  pack_rows(index = c("Part 2"))
+
+# 使用 kableExtra 的两列布局函数
+library(kableExtra)
+table_combined <- table1 %>% add_indent(levels = 1) %>%
+  column_spec(1, width = "5in") %>%
+  kable_styling(position = "float_left")
+
+table_combined2 <- table2 %>% add_indent(levels = 1) %>%
+  column_spec(1, width = "5in") %>%
+  kable_styling(position = "float_right")
+
+# 打印两个表格
+table_combined
+table_combined2
+
 ```
@@
 # Discussion {#sec-dis}
-What is done in this paper?
-What is something that we learn about the world?
-What is another thing that we learn about the world?
-What are some weaknesses of what was done?
-What is left to learn or how should we proceed in the future?
 
-## First discussion point {#sec-first-point}
+## What is done in this paper? {#sec-first-point}
 
@@
 
-## Second discussion point
+## What is something that we learn about the world?
 
-## Third discussion point
+## What is another thing that we learn about the world?
 
@@
 
-Weaknesses and next steps should also be included.
+Nevertheless, our result's prediction is surprisingly accompanied by recent economic conditions, suggesting a potential winning for the Conservative Party in the upcoming election.Our report relies on the assumption of complete trust in the authenticity of the data used; if responses are recorded in the survey or census showing fake information, it is impossible to eliminate the error caused by that misinformation.
+Meanwhile, accurate census data depicting the age distribution in the predicted year is essential.
+The percentage of different ages and the preference for different parties may vary throughout the years, leading to potential inaccuracies in our prediction.
+The exclusion of Quebec, Yukon, Northwest Territories, and Nunavut from our province variable, either due to distinct political parties within the province (Quebec) or missing data in our sources (Yukon et al.), limits the generalizability of our predictions of these regions.
+Furthermore, there are different economic conditions between the year of data collected and the year of the prediction.
+The variation of the economic situation could affect the outcomes of the winning party.Looking forward, analyzing the voting results within Quebec, Yukon, Northwest Territories, and Nunavut satisfies their unique provincial characteristic result better.
 
@@
 
-# References
+# References {#sec-ref}

### 2024-04-17 paper/paper.qmd
update

--- 2024-04-02 paper/paper.qmd
@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "Analysising how sociodemographic characteristics influence voting for the Liberal Party of Canada"
+subtitle: "Decoding CES 2021 Vote Data by using A Multilevel Logistic Regression Model"
 author: 
@@
 date-format: long
-abstract: "1) what was done, 2) what was found, and 3) why this matters (all at a high level). ."
+abstract: "This research utilized the 2021 Canadian Election Study and a multilevel logistic regression to examine how sociodemographic factors affect voting for the Liberal Party of Canada.
+It found that age, wealth, and education level significantly increase the likelihood of voting liberal, while children number, gender, and province do not.
+These results highlight the impact of life experiences and advantages on political ideologies and decision-making.
+Understanding these voting behaviors allows the Liberal Party of Canada to refine their electoral strategies, improving campaign effectiveness and voter engagement."
 format: pdf
+toc: true
 number-sections: true
 bibliography: references.bib
+link-citations: true
+output:
+  pdf_document: default
+
 ---
@@
 #| message: false
+library(tidyverse)
+library(here)
+library(tidyr)
+library(dplyr)
+library(arrow)
+library(ggplot2)
+library(kableExtra)
+library(bayesplot)
+library(rstanarm)
+library(modelsummary)
+library(lintr)
 
-library(tidyverse)
-library(arrow)
+library(lme4)
 ```
 
-```{r}
-#| label: cleaned
-#| warning: false
-#| message: false
-#| results: 'hide'
-#| echo: false
-
-analysis_data <- read_parquet("data/analysis_data/analysis_data.parquet")
-
+```{r include=FALSE, message=FALSE}
+# read the data file and store it in the variable
+analysis_data <- read_parquet(here("data", "analysis_data", "analysis_data.parquet"))
 ```
@@
 
-This report utilizes the 2021 Canadian Election Study data and the "General Social Survey, Cycle 31: Families, Public Use Microdata File Documentation and User's Guide" (Statistics Canada, 2019) to solve the emergent dilemma of diminishing vote participation rate.
-The primary purpose of this report is to use the data set to predict future voter turnout by differentiating throughout the province(note: not include Quebec, Yukon, Northwest Territories, and Nunavut).
+Voting decisions are at the heart of democratic societies, as they shape the composition of governments and determine the policies that govern our lives [@FIVD].
+To understand the main groups shaping Canada's political policies, this paper will focus on the demographic composition and behavioral patterns of the liberal voters historically  take up the majority of the voting [@sm].
 
-Based on previous voting analysis, the main factors affecting voting include age, education level, family status(represented by the number of children), and economic well-being(represented by the family income).
-("Factors Associated with Voting," 2015) Thus, the examination will focus on demographic variables, including age, gender, family income, education level, and the number of children in the vote rate corresponding to Canada's three main political parties.
-The three main political parties are Liberal, Conservative, and NDP(Canada's New Democrats), which occupied around 90 percent of the election 2010s.
-("Canadian Federal Election Results," n.d.) The report will use logistic regression on different parties to model the participation rate.
+Previous studies have often focused on broader demographic trends or isolated the effects of singular socioeconomic factors on voting behavior.
+However, there is a need for a more integrated analysis that considers how combinations of these factors interact to influence political orientation.
+This paper seeks to fill that gap by examining multiple variables simultaneously to provide a more comprehensive understanding of voter behavior.
+
+Based on prior voting analyses, key factors such as age, education level, family status (represented by the number of children), and economic well-being (indicated by family income) significantly influence voting behaviors [@Factors].
+To provide a more comprehensive view, gender will also be included as an influential factor in this study.
+Additionally, considering that Canada's population is concentrated in specific provinces, provincial distinctions will be accounted for as a random effects variable in our model.
+Notably, this study excludes Quebec, Yukon, Northwest Territories, and Nunavut due to distinct electoral dynamics in these regions.
+Under this method, we assume the authenticity of our source, 2021 Canadian Election Study data, to build up the multilevel logistic model.
+The provinces will serve as our random effects variable, assigning different intercepts to each province.
+This approach reflects the unique characteristics of each province, thereby enhancing the accuracy of our analysis.
 Whether the voting for particular parties or not will be recorded binary, as 1 or 0.
-Under this method, we assume the authenticity of our source, 2021 Canadian Election Study data, to build up the model.
+The estimand is the log-odds ratio of the effect of each explanatory variable on the probability of voting for the liberal party of Canada.
 
-The importance of this study is to reveal the complexities behind the recent decline in voter participation rates.
-By exploring the complex demographic factors and the voting rate of different political parties, this report could provide insights into the advantages of each of the three main parties during the election.
-According to past data, where liberals always take up the majority of the voting, we will assume the liberals will win the overall election.
-(Simon Fraser University, n.d.) Meanwhile, this report will examine how various demographic elements correlate with political affiliations, aiming to understand the challenges facing Canadian democracy comprehensively.
-In addition, the findings can not only predict the democratic participation rate throughout different states but also serve as a potential solution to the diminishing voting participation rate corresponding to each province, which can strengthen democracy throughout the nation.
+The analysis reveals a
 
-## estimand
-
- The paper introduces the basic information contains data source, methodology, variables and measurements in @sec-data.
-The visualization and analysis of the tendency differences in moderation by people across three social factors are presented in @sec-result.
+The remainder of this paper is structured as follows: the basic information contains data source, methodology, variables, measurements and the visualization of population structure and voting rate are in the @sec-data.
+The equation and interpretation of model are presented in @sec-models.
+The data and figure of coefficients are in the @sec-result.
 And in @sec-dis, we discuss what we have learned, our understanding of the world, the limitations, and the next steps of our research.
-@sec-app is for appendix and @sec-ref is listed all references in this paper.
+@sec-A is for appendix and @sec-ref is listed all references in this paper.
 
@@
 
-The survey data was sourced from the "2021 Canadian Election Study" (Stephenson, Harell, Rubenson, & Loewen, 2022), and the census information was obtained from the "General Social Survey, Cycle 31: Families, Public Use Microdata File Documentation and User’s Guide" (Statistics Canada, 2019).
+The Canadian Election Study (CES) is a world-class study of Canadian elections and related attitudes of key importance to the study and understanding of democratic processes and elections.
+In terms of global research stature, it is comparable to other national efforts such as the American National Election Studies and the British Election Study, among others.[@cesintro]
+
+## Measurement
+The CES 2021 was a comprehensive study conducted online, engaging a cohort of 20,968 participants selected from across Canada via the Leger Opinion panel.
+This bilingual survey, accommodating both English and French speakers, was open to individuals who were at least 18 years old and held Canadian citizenship or permanent residency.
+The study was methodically organized into two phases: the campaign period survey (CPS), which ran from August 17 to September 19, 2021, and the post-election survey (PES) carried out from September 23 to October 4, 2021.
+The CPS was subdivided into three parts—'CPS', 'CPS Modules', and 'CPS Oversample'—and these were ultimately merged into a single dataset.
+Participants from the CPS were invited to join the PES after the election concluded, with 15,069 individuals responding, resulting in a 72% response rate for the latter phase of the study.
 
 ## Analysis Tools
-Our paper applies using the statistical programming language R [@citeR].
-Besides the programming tool, we also employ the following packages: readr [@read], ggplot2 [@gg2], dplyr [@dpr], tidyverse [@tidy], MetBrewer [@met], knitr [@citeknr], tidyr[@tdr], kableExtra[@kbe] and grid[@grid].
+The data analysis performed by the statistical programming language `R` [@citeR].
+
+Besides the programming tool, we also employ the following packages: `here`[@here], `ggplot2`[@gg2], `dplyr` [@dp], `tidyverse` [@td], `tidyr`[@tdr], `kableExtra`[@kbe], `arrow`[@ar] and `lintr`[@ltr].
+
+The `rstanarm`[@R-rst] package was used to build the logistic multilevel linear regression model.
+`bayesplot`[@R-bys] was ustilized for Posterior predictive check and drawing R-hat figure in order to check the convergence of the MCMC algorithm.
+And `modelsummary`[@ms] was used for obtaining the coefficients of our model.
 
@@
 
->**Age**: include five different groups: 18-29 years old, 30-44 years old, 45-59 years old, 60-74 years old, and above 74 years old.
-We manipulate the age for census data, which has different years than the survey data.
+- **Age**:five age groups: 18-29 years old, 30-44 years old, 45-59 years old, 60-74 years old, and above 74 years old.
 
->**vote_liberal/vote_conservative/vote_NDP**: the voting result on whether to vote for three different parties. (Liberal, Conservative, or NDP) The result of voting or not is recorded in binary.
+- **vote_liberal/vote_conservative/vote_NDP**: the voting result on whether to vote for three different parties. (Liberal, Conservative, or NDP) The result of voting or not is recorded in binary.
 
->**Gender**: only include two types of gender, female and male, excluding non-binary or others
+- **Gender**: only include two types of gender, female and male, excluding non-binary or others
 
->**education_level**: including six different education levels(Less than high school, High school, Non-University, University certificate below the bachelor, Bachelor's degree, Above the bachelor).
+- **education_level**: including six different education levels from low to high: Less than high school, High school, Non-University, University certificate below the bachelor, Bachelor's degree, Above the bachelor.
 
->**family_income**: including six different groups. ("Less than 25,000", "25,000 to 49,999", "50,000 to 74,999", "75,000 to 99,999", "100,000 to 124,999", "125,000 and more")
+- **family_income**: including six different groups, from low to high:
+("Less than 25,000", "25,000 to 49,999", "50,000 to 74,999", "75,000 to 99,999", "100,000 to 124,999", "125,000 and more")
 
->**Province**: 9 different states and excluding Quebec, Yukon, Northwest Territories, and Nunavut.
+- **Province**: Ontario, Quebec, British Columbia, Alberta, Manitoba, New Brunswick, Newfoundland and Labrador, Nova Scotia, Prince Edward Island, Saskatchewan (excluding Quebec, Yukon, Northwest Territories, and Nunavut.)
+The corresponded short terms are ON, QC, BC, AB, MB, NB, NL, NS, PE, SK.
 
@@
 
+\newpage
+
 ## Sample of cleaned data
+```{r}
+#| label: tbl-cleaned
+#| tbl-cap: Sample of the Cleaned Data
+#| warning: false
+#| echo: false
 
-## Measurement
-The CES 2021, consisting of an online cohort of 20,968 participants from the broader Canadian populace, was facilitated via the Leger Opinion panel.
-This study was structured in two distinct stages: the campaign period survey (CPS) and the post-election survey (PES).
-The CPS phase was further divided into three segments – "CPS", "CPS Modules", and "CPS Oversample", which were later consolidated into one dataset.
-Regarding the PES, all individuals who participated in the CPS were invited back for this subsequent survey after the election.
-Out of these, 15,069 individuals completed the PES, marking a response rate of 72%.
+head(analysis_data, 5) |>
+  kable(
+    col.names = c("age", "vote_liberal", "vote_conservative", "vote_NDP","gender","education_level","family_income","province","children_number"),
+    booktabs = TRUE
+  )%>%
+  kable_styling(latex_options = c("scale_down"))
+
+```
 
@@
 
-distribution of age, gender, income, education level, province, children number
+### The Population Structure in sociodemographic characteristics
+```{r, fig.width=10, fig.height=6}
+#| echo: false
+#| eval: true
+#| label: fig-percent
+#| fig-cap: Population Percentage of different groups in a category
+#| warning: false
 
-# Model
+# Set a copy of analysis data, in order to shorten categories' names
+analysis_data_2 <- analysis_data
+labels_province <- c("Ontario" = "ON", "Quebec" = "QC", "British Columbia" = "BC", "Alberta" = "AB",
+                     "Manitoba" = "MB", "New Brunswick" = "NB", "Newfoundland and Labrador" = "NL",
+                     "Nova Scotia" = "NS", "Prince Edward Island" = "PE", "Saskatchewan" = "SK")
 
-The goal of our modelling strategy is twofold. Firstly,...
+analysis_data_2 <- analysis_data_2 %>%
+  mutate(province = recode(province, !!!labels_province))
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+labels_income <- c("Less than $25,000" = "<25k", "$25,000 to $49,999"= "25~50k","$50,000 to $74,999" = "50~75k","$75,000 to $99,999" = "75~100k","$100,000 to $124,999" = "100~125k","$125,000 and more" = ">125k")
+
+analysis_data_2 <- analysis_data_2 %>%
+  mutate(family_income = recode(family_income, !!!labels_income))
+
+labels_education <- c(
+  "Less than high school" = "Below HS",
+  "High school" = "HS Grad",
+  "Non-University" = "Non-Uni",
+  "University certificate below the bachelor" = "Uni Cert",
+  "Bachelor's degree" = "Bachelor",
+  "Above the bachelor" = "Post-Bach"
+)
+
+analysis_data_2 <- analysis_data_2 %>%
+  mutate(education_level = recode(education_level, !!!labels_education))
+
+# Define a function to calculate percentages for each category within a variable
+calculate_percentage <- function(data, category) {
+  data %>%
+    count(!!sym(category)) %>%
+    mutate(percentage = n / sum(n) * 100) %>%
+    rename(Category = !!sym(category)) %>%
+    mutate(Variable = category)  # store the variable name
+}
+
+# Apply the function to each of the variables
+# calculate each category's percentage it took in each group
+
+category_list = c("age", "gender", "family_income", "education_level", "province", "children_number")
+percentages <- lapply(category_list, calculate_percentage, data = analysis_data_2)
+
+# Combine the list of data frames into one data frame
+percentages_df <- bind_rows(percentages)
+
+income_levels_order <- c("<25k","25~50k","50~75k","75~100k","100~125k",">125k")
+percentages_df <- percentages_df %>%
+  mutate(Category = if_else(Variable == "family_income", factor(Category, levels = income_levels_order), as.factor(Category)))
+
+educ_levels_order <- c("Below HS","HS Grad", "Non-Uni","Uni Cert","Bachelor","Post-Bach")
+percentages_df <- percentages_df %>%
+  mutate(Category = if_else(Variable == "education_level", factor(Category, levels = educ_levels_order), as.factor(Category)))
+
+# Generate the plot
+combined_plot <- ggplot(percentages_df, aes(x = Category, y = percentage, fill = Variable)) +
+  geom_bar(stat = "identity") +
+  facet_wrap(~Variable, scales = "free_x") + # allows each facet to have its own x axis
+  labs( y = "Percentage of Total") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 25, hjust = 1)) +
+  scale_fill_brewer(palette = "Set1")
+
+# Print the combined plot
+combined_plot
+
+```
+@fig-percent shows the proportion of the population within each subcategory to the population of the entire category after categorizing all voters according to six different demographic categories.
+
+The demographic data indicates that the majority of the population falls within the age range of 60 to 74 years, accounting for approximately 30% of the sample.
+
+Regarding family structure, 40% of individuals do not have children, which includes those who are unmarried, while a two-child family configuration is the next most prevalent, representing 30% of the sample.
+
+In terms of educational attainment, the predominant qualification is a bachelor's degree. High school graduates and individuals without a university degree each make up about 20% of the population.
+
+As for household income, the distribution appears relatively uniform across different brackets, with a notable concentration of individuals earning between 50k to 75k and those earning more than 125k, both groups constituting about 20%.
+
+The gender composition of the population is slightly skewed towards women, who make up just over 50%, while men represent a marginally lower proportion, just above 40%.
+
+Geographically, a significant portion of the electorate, around 50%, resides in Ontario, reflecting a centralization of voters in this province.
+
+### The vote rate for three main parties
+```{r, fig.width=10, fig.height=6}
+#| echo: false
+#| eval: true
+#| label: fig-vote-percent
+#| fig-cap: Percentage of Voting for 3 parties in different groups
+#| warning: false
+survey_long <- analysis_data_2 %>%
+  pivot_longer(cols = starts_with("vote_"), 
+               names_to = "party", 
+               values_to = "vote") %>%
+  pivot_longer(cols = c("age", "gender", "family_income", "education_level", "province", "children_number"),
+               names_to = "category",
+               values_to = "group") %>%
+  group_by(category, group, party) %>%
+  summarise(vote_percent = mean(vote, na.rm = TRUE), .groups = 'drop') %>%
+  ungroup()
+
+survey_long <- survey_long %>%
+  mutate(group = case_when(
+    category == "family_income" & group %in% c("<25k","25~50k","50~75k","75~100k","100~125k",">125k") ~ factor(group, levels = c("<25k","25~50k","50~75k","75~100k","100~125k",">125k")),
+    category == "education_level" & group %in% c("Below HS","HS Grad", "Non-Uni","Uni Cert","Bachelor","Post-Bach") ~ factor(group, levels = c("Below HS","HS Grad", "Non-Uni","Uni Cert","Bachelor","Post-Bach")),
+    TRUE ~ as.factor(group)
+  ))
+
+ggplot(survey_long, aes(x = group, y = vote_percent, color = party, group = party)) +
+  geom_line() + 
+  geom_point() + 
+  scale_color_manual(values = c("vote_liberal" = "red","vote_conservative" = "grey","vote_NDP" = "lightblue")) +
+  labs(x = "Group", 
+       y = "Percentage", 
+       color = "Party") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 25, hjust = 1)) +
+  facet_wrap(~category, scales = "free_x", ncol = 2)
+
+```
+@fig-vote-percent displays the probability of voters voting for three main parties (the Liberal, the Conservative and the NDP) within each subcategory (e.g.
+'18-29') under six different demographic categories (e.g.
+'age'), after classifying all voters according to these demographic categories.
+
+Age: There appears to be a positive correlation between age and the percentage of votes for the Liberal party.
+As voters age, from the young demographic of 18-29 to those over 75, support for the Liberals seems to steadily rise from about 50% to just over 50%.
+
+Education Level: From the lowest to the highest education levels, support for the Liberal party shows a relatively stable trend with a slight increase.
+Those with a bachelor's degree appear to be the most steadfast in their support for the Liberals, with a support rate above 40%.
+
+Gender: Female voters show higher support for the Liberal party than males, indicating that gender may be a significant factor in support for the Liberals.
+
+Number of Children: Families with more children seem to be more inclined to support the Liberal party, especially when there are four or more children, where the support rate peaks at about 45%.
+
+Family Income: The Liberal party enjoys higher support in the middle-income brackets, while there is a decline in support among the higher income bracket (over 125k).
+
+Province: Support for the Liberals is significantly higher in Ontario (ON) than in other provinces, possibly indicating the impact of regional factors on support for the Liberal party.
+
+# Model {#sec-models}
 
@@
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
-
 $$ log(\frac{p_{ij}}{1-p_{ij}}) = \beta_{0j}+\beta_1  x_{ij\ age} + \beta_2 x_{ij\ gender} + \beta_3  x_{ij\ education\ level} + \beta_4  x_{ij\ family\ income} + \beta_5  x_{ij\ children\ number}$$
@@
 
+### Model justification
 In the model, $j$ is the province and $i$ is the individual voter indicator.
@@
 
-$log(\frac{p_{ij}}{1-p_{ij}})$ means the log of odds of voting for
- any specific party.\
+Log Odds: The formula $log(\frac{p_{ij}}{1-p_{ij}})$ calculates the log odds of a voter choosing a specific party, effectively quantifying how likely they are to vote for the party versus not voting for it.\
 
-$\beta_0$ represents the intercept of the model and is the log of odds
-of voting for any specific party when the individual is at a certain age,
-with a certain gender, education level, family income and children
-number.\
+Intercept ($\beta_0$ and $\beta_{0j}$): The intercept, $\beta_0$, is the baseline log odds of voting for the party across all voters, assuming average conditions for all explanatory variables (age, gender, etc.).\ $\beta_{0j}$ adjusts this intercept for each province, capturing local variations and assuming these effects are normally distributed.\
 
-$\beta_{0j}$ stands for jth province effect on the log of odds of voting for
-any specific party, and we assume the intercept $\beta_{0j}$ in different
-provinces is random and follows a normal distribution with mean
-$\mu_{\beta_{0}}$ and variance $\sigma^2_{\beta_{0}}$.\
+Slopes ($\beta_1, \beta_2, \beta_3, \beta_4, \beta_5$):
 
-$\beta_1$ represents the slope of age level in the model, then for any voter,
-one unit increase in age, we expect a $\beta_1$ increase in log odds of
-voting for any specific party. $\beta_2$ represents the average difference in
-log odds of voting for any specific party between Males and Females for a
-certain age, education level, family income and children number.\
+$\beta_1$: Change in log odds of voting for the party with each additional year of a voter’s age.\
+$\beta_2$: Difference in log odds between male and female voters, adjusting for other factors.\
+$\beta_3$: Difference in log odds among education levels, controlling for other variables.\
+$\beta_4$: Difference in log odds among various family income levels.\
+$\beta_5$: Difference in log odds based on the number of children in the family.\
 
-$\beta_3$ represents the average difference in log odds of voting for
-any specific party between groups with different education levels for a
-certain age, gender, family income and children number.\
+Variables ($x_{ij}$): Represents categorical predictors such as age, gender, education, income, and number of children for voter $i$ in province $j$, where each variable is coded as 0 or 1.\
 
-$\beta_4$ represents the average difference in log odds of voting for
-any specific party between groups with different family income levels for a certain
-age, gender, education level and children number.\
+# Results {#sec-result}
 
-$\beta_5$ represents the average difference in log odds of voting for
-any specific party between groups with different children number levels for a
-certain age, gender, education level and family income.\
+```{r}
+#| label: models
+#| warning: false
+#| message: false
+#| echo: false
 
-$x_{ij}$ is a binary variable, it can only be 1 or 0 as all the variables we have are categorical, it also stands for the ith voter in jth province.
+liberal_model <- readRDS("../models/liberal_model.rds")
+```
 
-### Model justification
+## Model Coefficients
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
-
-# Results
-
-```{r echo=FALSE}
-# Retrieve the Bayesian linear model from the saved .rds file
-liberal_model <- readRDS(file = "models/liberal_model.rds")
+```{r}
+#| label: tbl-liberal
+#| tbl-cap: Summary Statistics of the Coefficients of the Linear Model
+#| warning: false
+#| echo: false
+modelsummary(liberal_model, output = "kableExtra")
 
@@
 
-# Discussion
-What is done in this paper?
-What is something that we learn about the world?
-What is another thing that we learn about the world?
-What are some weaknesses of what was done?
-What is left to learn or how should we proceed in the future?
+@tbl-liberal provides key coefficients to understand the relationship between variables and possibility of voting for the Liberal Party:
 
-## First discussion point {#sec-first-point}
+- **Intercept**: The model's intercept is estimated at approximately -1.871.
+indicating the log odds of voting for the Liberal Party when all other explanatory variables are at their reference levels, and the random effect of province is at its average level.
+A negative intercept suggests that without any other influences, the likelihood of not voting for the Liberal Party is higher than voting for it.
+- **age groups**: The increasing coefficients indicates that, compared to the reference age group (usually the youngest group), the odds of voting for the Liberal Party increase with age.
+- **gender**: The coefficient for Male is -0.030, suggesting a slightly lower likelihood for males to support the Liberal Party compared to females, assuming females are the reference category.
+- **education levels**: The coefficients imply that individuals with higher educational qualifications, particularly those with a bachelor's degree (0.702) or higher (0.734), are more likely to vote for the Liberal Party compared to those without a high school diploma.
+- **family income**: Higher-income families being more likely to vote for the Liberal party.
+- **number of children**: The coefficients for number of children are negative, except for children_number1, meaning that households with children are less likely to vote for the Democratic Party compared to those without children.
+- **random effect for province**: (Sigma[province × (Intercept),(Intercept)]) is valued at 0.186, indicating variability among intercepts across provinces, reflecting differences in voting behaviors among provinces.
+- **Other statistical measures**: the number of observations (Num.Obs.) at 3310, the R² value at 0.060, and the Marginal R² (R² Marg.) at 0.042, suggesting that the model explains a modest amount of the variability overall.
+The model's log-likelihood (Log.Lik.) is -2066.231, which describes the probability of the model fitting the data.
+ELPD and LOOIC are criteria used for model selection and comparison, while the Root Mean Square Error (RMSE) is a measure of the model's predictive accuracy with a value of 0.47, where lower values indicate more accurate predictions.
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+```{r}
+#| label: fig-liberal
+#| tbl-cap: Coefficients of social factors influence vote for liberal party
+#| warning: false
+#| echo: false
 
-## Second discussion point
+modelplot(liberal_model, conf_level = 0.9) +
+  labs(x = "90 per cent credibility interval")
 
-## Third discussion point
+```
+@fig-liberal is a statistical model's coefficient estimate graph, which demonstrates the impact of different variables on the probability of voting for the Liberal Party.
+Each row represents the coefficient of a variable in the model, with the point estimate of the coefficient represented by a solid black dot and its 90% credibility intervals (Credibility Intervals) represented by black lines.
+The point estimate of the coefficient (black dot) indicates the trend of the response variable (here, the probability of voting for the Liberal Party) when that variable increases by one unit.
+If the black dot is to the right of the zero line, it suggests that an increase in this variable may increase the probability of voting for the Liberal Party; if it is to the left, it may decrease the probability.
+
+The width of the 90% credibility intervals (horizontal lines) reflects the uncertainty of the estimate.
+If the interval is narrow, it suggests a higher certainty about the impact of this variable.
+If the interval is wide, it suggests a greater uncertainty in the estimate.
+If the 90% credibility interval does not contain zero, then we can consider that at the 90% confidence level, the variable has a significant impact on voting behavior.
+If the interval includes zero, we cannot confirm its impact at this level.
+
+For instance, the credibility interval for 'genderMale' is quite narrow and does not contain zero.
+This suggests that the effect of being male on the probability of voting for the Liberal Party is estimated with higher certainty and is statistically significant at the 90% confidence level.
+The fact that the interval does not include zero implies that there is a discernible impact of gender on voting behavior.
+For Family Income (50,000 to 74,999), its interval is wider, suggesting that there's more uncertainty regarding the impact of this income level on the probability of voting for the Liberal Party.
+However, since the interval does not include zero, it suggests that there is likely a significant impact, but the exact magnitude of this effect is less certain.
+
+```{r}
+#| label: tbl-liberal-3
+#| tbl-cap: Coefficients of Liberal Party Model In Different Province
+#| warning: false
+#| echo: false
+#Coefficient table of model_liberal
+a = coef(liberal_model)
+b <- a$province 
+b%>%
+select(c(1:1))%>%
+kable()
+
+```
+@tbl-liberal-3 shows the intercept for each province. The coefficients confirms our prediction from checking the percentage of voting for the liberal party in data section.
+
+\newpage
+# Discussion {#sec-dis}
+
+## What is done in this paper? {#sec-first-point}
+In the paper, researchers conducted an in-depth analysis of Canadian voter behavior using a multilevel logistic regression model, specifically focusing on voters of the Liberal Party.
+They utilized data from the 2021 Canadian Election Study (CES), examining how factors such as age, education level, family income, gender, and the number of children influence voting support for the Liberal Party.
+Provinces were included as random effects variables in the model to account for political variations across regions.(exclude regions like Quebec, Yukon, Northwest Territories, and Nunavut due to their unique electoral dynamics.)
+
+## What we learn about the world?
+Through this study, we identified age, education level, economic status, and gender as significant factors influencing voter support for the Liberal Party.
+As age increases, voter support for the Liberal Party tends to increase as well, suggesting that older voters may prefer parties that promote stable policies and emphasize social welfare.
+Moreover, voters with higher education levels tend to support the Liberal Party, likely reflecting their approval of the party’s policies on education, environmental protection, and technological innovation.
+Similarly, the Liberal Party finds strong support among high-income groups, possibly due to the party's policies promoting economic development and business innovation.
+
+Based on these findings, policymakers and the Liberal Party should consider developing specific policies to attract and maintain the support of these key voter groups.
+For instance, they could increase discussions on retirement insurance and health protection to appeal to older voters; continue supporting educational and research projects to solidify support among highly educated voters; and maintain support from high-income groups through tax incentives and business support strategies.
+Additionally, strengthening support for women's rights could also help to increase female voter turnout for the Liberal Party.
 
@@
 
-Weaknesses and next steps should also be included.
+Although the model is sufficiently convergence in diagnostics section, the report relies on the assumption of complete trust in the authenticity of the data used; if responses are recorded in the survey or census showing fake information, it is impossible to eliminate the error caused by that misinformation.
+Meanwhile, accurate census data depicting the age distribution in the predicted year is essential.
+The percentage of different ages and the preference for different parties may vary throughout the years, leading to potential inaccuracies in our prediction.
+The exclusion of Quebec, Yukon, Northwest Territories, and Nunavut from our province variable, either due to distinct political parties within the province (Quebec) or missing data in our sources (Yukon et al.), limits the generalizability of our predictions of these regions.
+Furthermore, there are different economic conditions between the year of data collected and the year of the prediction.
+The variation of the economic situation could affect the outcomes of the winning party.
+
+In addition, the relatively limited explanatory power of our model (R² value of 0.060) suggests that there are other factors that are not captured by the model that may be influencing voters' voting behavior.
+Future research could explore additional variables such as cultural orientation, social identity, and recent political events, all of which may have a significant impact on voter behavior.
+
+Looking forward, analyzing the voting results within Quebec, Yukon, Northwest Territories, and Nunavut satisfies their unique provincial characteristic result better.
 
@@
 
-## Posterior predictive check
+## Posterior predictive check {#sec-posterior}
+
+```{r fig-posterior-plot, echo=FALSE, fig.cap="pp check"}
+
+pp_check(liberal_model) + 
+  theme_classic() +
+  theme(legend.position = "bottom")
+```
+
+In @fig-posterior-plot, we implement a posterior predictive check.
+This shows the simulated data from the posterior distribution (illustrated by the lighter lines) aligns closely with the distribution of the observed data (indicated by the solid line).
+The lighter lines, which represent the uncertainty in our predictions, nearly converge with the solid line.
+This convergence suggests that our model accurately fits the observed data, indicating that the selected priors and model structure effectively capture the variations in voting for the Liberal Party among interviewees.
 
@@
 
+```{r, fig.width=10, fig.height=5}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-rhat
+#| fig-cap: "Checking the convergence of the MCMC algorithm"
+plot(liberal_model, "rhat")
+```
+
+In @fig-rhat, the distribution of R-hat values is displayed, which is used in Bayesian statistics to assess convergence.
+Different R̂ values are represented by circles of different colors.
+Blue circles represent R̂ values that do not exceed 1.05, which is typically considered an acceptable level of convergence; light blue circles indicate R̂ values between 1.05 and 1.1, which may suggest the need for more samples or further investigation; and dark blue circles represent R̂ values greater than 1.1, which usually indicates insufficient convergence, requiring longer chains, more samples, or model improvements.
+This result suggests that there are no convergence issues in this particular Bayesian model estimation.
+All points are tightly concentrated around the standard line of 1.00, which is a very positive sign.
+
 \newpage
 
-# References
+# References {#sec-ref}

### 2024-04-17 scripts/03-test_data.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Test data
+# Purpose: Test cleaned data
 # Author: Yichen Ji
 # Date: 27 March 2024
 # Contact: yic.ji@mail.utoronto.ca

### 2024-04-17 scripts/04-model.R

@@ -4,19 +4,28 @@
 # Date: 27 March 2024
 # Contact: yic.ji@mail.utoronto.ca
 # License: MIT
-# Pre-requisites:
+# Pre-requisites:download packages tidyverse, rstanarm and arrow
 # Any other information needed? None
 
 #### Workspace setup ####
 library(tidyverse)
 library(rstanarm)
-
-#### Read data ####
 library(arrow)
 
+
+#### Read data ####
 analysis_data <- read_parquet("data/analysis_data/analysis_data.parquet")
 
 ### Model data ####
+
+#Reorder the categories in education level group
+analysis_data$education_level <- factor(analysis_data$education_level,
+                                        levels = c("Less than high school", 
+                                                   "High school", 
+                                                   "Non-University",
+                                                   "University certificate below the bachelor", 
+                                                   "Bachelor's degree", 
+                                                   "Above the bachelor"))
 
 liberal_model <- stan_glmer(
   vote_liberal ~ age + gender + education_level + family_income + children_number + (1 | province),
@@ -30,35 +39,8 @@ liberal_model <- stan_glmer(
   control = list(adapt_delta = 0.99)
 )
 
-summary(liberal_model)
-
+#Save the model
 saveRDS(liberal_model, file = "models/liberal_model.rds")
 
-conservative_model <- stan_glmer(
-  vote_conservative ~ age + gender + education_level + family_income + children_number + (1 | province),
-  data = analysis_data,
-  family = binomial(link = "logit"),
-  prior = normal(0, 2.5, autoscale = TRUE), 
-  prior_intercept = normal(0, 2.5, autoscale = TRUE), 
-  seed = 2024,
-  chains = 4,
-  cores = 4,
-  control = list(adapt_delta = 0.99)
-)
-summary(conservative_model)
-saveRDS(conservative_model, file = "models/conservative_model.rds")
 
 
-NDP_model <- stan_glmer(
-  vote_NDP ~ age + gender + education_level + family_income + children_number + (1 | province),
-  data = analysis_data,
-  family = binomial(link = "logit"),
-  prior = normal(0, 2.5, autoscale = TRUE), 
-  prior_intercept = normal(0, 2.5, autoscale = TRUE), 
-  seed = 2024,
-  chains = 4,
-  cores = 4,
-  control = list(adapt_delta = 0.99)
-)
-summary(NDP_model)
-saveRDS(NDP_model, file = "models/NDP_model.rds")

### 2024-04-17 scripts/05-model_api.R

@@ -1,0 +1,45 @@
+
+library(arrow)
+liberal_model <- readRDS("../models/liberal_model.rds")
+
+# Enhancement: API for the linear model
+#install.packages("plumber")
+library(plumber)
+
+#* @apiTitle Liberal Vote Prediction API
+#* @apiDescription This API predicts the probability of voting liberal based on the model.
+
+#* @param age The age of the individual.
+#* @param gender The gender of the individual.
+#* @param education_level The education level of the individual.
+#* @param family_income The family income of the individual.
+#* @param children_number The number of children in the individual's family.
+#* @param province The province of the individual.
+#* @post /predict_liberal_vote
+
+function(age, gender, education_level, family_income, children_number, province) {
+  # Convert parameters to the correct type
+  age <- as.numeric(age)
+  gender <- as.factor(gender)
+  education_level <- as.factor(education_level)
+  family_income <- as.numeric(family_income)
+  children_number <- as.numeric(children_number)
+  province <- as.factor(province)
+  
+  # Create a new data frame for prediction
+  new_data <- data.frame(age = age,
+                         gender = gender,
+                         education_level = education_level,
+                         family_income = family_income,
+                         children_number = children_number,
+                         province = province)
+  
+  # Make prediction using the `liberal_model`
+  prediction <- predict(liberal_model, newdata = new_data, type = "response")
+  
+  # Return the prediction
+  return(list(prediction = prediction))
+}
+
+
+plumb("05-model_api.R")$run(port=8000)

### 2024-04-17 scripts/lintr.R

@@ -1,0 +1,16 @@
+#### Preamble ####
+# Purpose: Set package lintr to check code
+# Author: Yichen Ji
+# Date: 27 March 2024
+# Contact: yic.ji@mail.utoronto.ca
+# License: MIT
+# Pre-requisites:NA
+# Any other information needed? None
+
+
+#install.packages("lintr")
+
+library(lintr)
+
+# Lint through all the scripts in the current directory
+lint_dir(path = ".")

### 2024-04-17 scripts/05-model_api.R
update

@@ -1,24 +1,23 @@
 
-library(arrow)
+# 加载必要的库
+library(plumber)
+library(rstanarm)
+
+# 读取模型，这里假设模型文件在当前目录
 liberal_model <- readRDS("../models/liberal_model.rds")
 
-# Enhancement: API for the linear model
-#install.packages("plumber")
-library(plumber)
-
 #* @apiTitle Liberal Vote Prediction API
-#* @apiDescription This API predicts the probability of voting liberal based on the model.
-
-#* @param age The age of the individual.
-#* @param gender The gender of the individual.
-#* @param education_level The education level of the individual.
-#* @param family_income The family income of the individual.
-#* @param children_number The number of children in the individual's family.
-#* @param province The province of the individual.
+#* @apiDescription This API predicts the probability of voting for the Liberal Party based on the model.
+#* @param age numeric The age of the individual.
+#* @param gender character The gender of the individual.
+#* @param education_level character The education level of the individual.
+#* @param family_income numeric The family income of the individual.
+#* @param children_number numeric The number of children in the individual's family.
+#* @param province character The province of the individual.
 #* @post /predict_liberal_vote
-
 function(age, gender, education_level, family_income, children_number, province) {
-  # Convert parameters to the correct type
+  
+  # 确保输入参数是正确的类型
   age <- as.numeric(age)
   gender <- as.factor(gender)
   education_level <- as.factor(education_level)
@@ -26,7 +25,7 @@ function(age, gender, education_level, family_income, children_number, province)
   children_number <- as.numeric(children_number)
   province <- as.factor(province)
   
-  # Create a new data frame for prediction
+  # 创建一个新的数据框架进行预测
   new_data <- data.frame(age = age,
                          gender = gender,
                          education_level = education_level,
@@ -34,12 +33,13 @@ function(age, gender, education_level, family_income, children_number, province)
                          children_number = children_number,
                          province = province)
   
-  # Make prediction using the `liberal_model`
-  prediction <- predict(liberal_model, newdata = new_data, type = "response")
+  # 使用模型进行预测
+  prediction <- posterior_predict(liberal_model, newdata = new_data)
   
-  # Return the prediction
+  # 返回预测结果
   return(list(prediction = prediction))
 }
 
-
-plumb("05-model_api.R")$run(port=8000)
+# 创建一个plumber API
+pr <- plumb("05-model_api.R") # 假设这是你的脚本文件名
+pr$run(port=8000)

### 2024-04-17 scripts/05-model_api.R
update

@@ -1,31 +1,32 @@
-
-# 加载必要的库
+# Load necessary libraries
 library(plumber)
 library(rstanarm)
+library(arrow)
 
-# 读取模型，这里假设模型文件在当前目录
-liberal_model <- readRDS("../models/liberal_model.rds")
+# Assuming your stan_glmer model is saved as 'liberal_model.rds'
+# Load your previously saved stan_glmer model
+liberal_model <- readRDS(".../models/liberal_model.rds")
 
-#* @apiTitle Liberal Vote Prediction API
-#* @apiDescription This API predicts the probability of voting for the Liberal Party based on the model.
-#* @param age numeric The age of the individual.
-#* @param gender character The gender of the individual.
-#* @param education_level character The education level of the individual.
-#* @param family_income numeric The family income of the individual.
-#* @param children_number numeric The number of children in the individual's family.
-#* @param province character The province of the individual.
-#* @post /predict_liberal_vote
+#* @apiTitle Voting Prediction API
+#* @apiDescription This API predicts the likelihood of an individual voting for the Liberal Party based on a statistical model.
+
+#* @param age The age of the individual.
+#* @param gender The gender of the individual: 'male', 'female', or other categories if applicable.
+#* @param education_level The highest education level of the individual.
+#* @param family_income The annual family income of the individual.
+#* @param children_number The number of children in the individual's family.
+#* @param province The province of the individual.
+#* @post /predictVote
 function(age, gender, education_level, family_income, children_number, province) {
-  
-  # 确保输入参数是正确的类型
-  age <- as.numeric(age)
+  # Convert parameters to the correct type
+  age <- as.factor(age)
   gender <- as.factor(gender)
   education_level <- as.factor(education_level)
-  family_income <- as.numeric(family_income)
-  children_number <- as.numeric(children_number)
+  family_income <- as.factor(family_income)
+  children_number <- as.factor(children_number)
   province <- as.factor(province)
   
-  # 创建一个新的数据框架进行预测
+  # Create a new data frame for prediction
   new_data <- data.frame(age = age,
                          gender = gender,
                          education_level = education_level,
@@ -33,13 +34,15 @@ function(age, gender, education_level, family_income, children_number, province)
                          children_number = children_number,
                          province = province)
   
-  # 使用模型进行预测
[…]

### 2024-04-17 paper/paper.qmd
update

@@
 ---
-title: "Analysising how sociodemographic characteristics influence voting for the Liberal Party of Canada"
+title: "Analyzing how sociodemographic characteristics influence voting for the Liberal Party of Canada"
 subtitle: "Decoding CES 2021 Vote Data by using A Multilevel Logistic Regression Model"
@@
   pdf_document: default
+header-includes:
+      - \usepackage{float}
+      - \floatplacement{table}{H}
 
@@
 
-The analysis reveals a
+The analysis reveals age, wealth, and education level have a positive relationship with voting liberal, while children number, gender, and province do not.
 
@@
 And in @sec-dis, we discuss what we have learned, our understanding of the world, the limitations, and the next steps of our research.
-@sec-A is for appendix and @sec-ref is listed all references in this paper.
+@sec-A contains pp check and r-hat check for the model and @sec-ref is listed all references in this paper.
 
@@
 ```
-@tbl-liberal-3 shows the intercept for each province. The coefficients confirms our prediction from checking the percentage of voting for the liberal party in data section.
+@tbl-liberal-3 shows the intercept for each province. The coefficients align with the trend illustrated in @fig-vote-percent.
 
-\newpage
 # Discussion {#sec-dis}
@@
 ## What we learn about the world?
-Through this study, we identified age, education level, economic status, and gender as significant factors influencing voter support for the Liberal Party.
-As age increases, voter support for the Liberal Party tends to increase as well, suggesting that older voters may prefer parties that promote stable policies and emphasize social welfare.
-Moreover, voters with higher education levels tend to support the Liberal Party, likely reflecting their approval of the party’s policies on education, environmental protection, and technological innovation.
-Similarly, the Liberal Party finds strong support among high-income groups, possibly due to the party's policies promoting economic development and business innovation.
+Through this study, we have gained a nuanced understanding of the factors that influence voter support for the Liberal Party in Canada.
+As individuals age, their likelihood to support the Liberal Party increases, a trend particularly noticeable among older voters who have traditionally been Conservative supporters.
+This shift could be attributed to the Liberal Party's efforts in addressing issues pertinent to senior citizens, possibly influenced by recent events such as the COVID-19 vaccination rollout, where a significant percentage of senior Canadians have been vaccinated.
+The implication here is that policies that directly impact the well-being and concerns of older adults can be a powerful determinant of their voting preferences.
 
-Based on these findings, policymakers and the Liberal Party should consider developing specific policies to attract and maintain the support of these key voter groups.
-For instance, they could increase discussions on retirement insurance and health protection to appeal to older voters; continue supporting educational and research projects to solidify support among highly educated voters; and maintain support from high-income groups through tax incentives and business support strategies.
-Additionally, strengthening support for women's rights could also help to increase female voter turnout for the Liberal Party.
+Furthermore, analysis of voting intentions suggests that gender plays a significant role among younger voters, where we see distinct patterns such as young men favoring the Conservative Party and young women showing stronger support for the NDP.
+Yet, for the Liberal Party, the support appears to be consistent across different segments, irrespective of age or gender.
+This consistency suggests that the Liberal Party's policies may have broad appeal across different demographics or that the party's stance on various issues is not polarizing enough to create a noticeable gender gap within its supporters.
+
+Educational attainment is another influential factor, with those holding higher education levels likely resonating with the Liberal Party's emphasis on education, environmental protection, and technological innovation.
+These voters may view the Liberal Party as more aligned with their values and interests, particularly in policy areas that affect long-term societal progress.
+
+Given these insights, it would be beneficial for policymakers and the Liberal Party to focus on developing and communicating policies that address the specific needs and concerns of these key voter groups.
+For the older demographic, continuing to provide and expand on healthcare, retirement insurance, and health protection will likely be vital.
+For the highly educated demographic, emphasizing the Liberal Party's commitment to advancing education and innovation could solidify support.
+Additionally, understanding the salient issues for different age and gender groups can help tailor communication and policy initiatives more effectively.
+
+These observations are crucial for the Liberal Party if they are to maintain and strengthen their voter base, especially considering the evolving dynamics within the Canadian electorate.
 
@@
 # Appendix {#sec-A}
-
-# Additional data details
-
-# Model details {#sec-model-details}
 

### 2024-04-17 scripts/05-model_api.R
update

@@ -5,7 +5,8 @@ library(arrow)
 
 # Assuming your stan_glmer model is saved as 'liberal_model.rds'
 # Load your previously saved stan_glmer model
-liberal_model <- readRDS(".../models/liberal_model.rds")
+
+liberal_model <- readRDS("../models/liberal_model.rds")
 
 #* @apiTitle Voting Prediction API
 #* @apiDescription This API predicts the likelihood of an individual voting for the Liberal Party based on a statistical model.
@@ -41,8 +42,7 @@ function(age, gender, education_level, family_income, children_number, province)
   return(list(prediction = prediction))
 }
 
-# Run the API
 #* @plumber
 function(pr) {
-  pr$run(port=8000)
+  pr
 }

### 2024-04-17 scripts/04-model.R
update

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Models for predicting 2024 Canadian election
+# Purpose: Build a multi-level logistic linear regression model for the Liberal Party in CES2021
 # Author: Yichen Ji
 # Date: 27 March 2024
 # Contact: yic.ji@mail.utoronto.ca
@@ -11,7 +11,7 @@
 library(tidyverse)
 library(rstanarm)
 library(arrow)
-
+library(plumber)
 
 #### Read data ####
 analysis_data <- read_parquet("data/analysis_data/analysis_data.parquet")
@@ -41,6 +41,4 @@ liberal_model <- stan_glmer(
 
 #Save the model
 saveRDS(liberal_model, file = "models/liberal_model.rds")
-
-
 

### 2024-04-17 scripts/05-model_api.R

@@ -1,3 +1,14 @@
+#### Preamble ####
+# Purpose: Build API for the Liberal Model
+# Author: Yichen Ji
+# Date: 27 March 2024
+# Contact: yic.ji@mail.utoronto.ca
+# License: MIT
+# Pre-requisites:download packages plumber, rstanarm and arrow
+# Any other information needed? None
+
+
+
 # Load necessary libraries
 library(plumber)
 library(rstanarm)
@@ -36,10 +47,14 @@ function(age, gender, education_level, family_income, children_number, province)
                          province = province)
   
   # Make prediction using the `liberal_model`
-  prediction <- posterior_predict(liberal_model, newdata = new_data)
+  simulated_predictions <- posterior_predict(liberal_model, newdata = new_data)
   
-  # Return the prediction
-  return(list(prediction = prediction))
+  # Calculate the mean of the simulated predictions
+  mean_prediction <- mean(simulated_predictions)
+  
+  # Return the mean prediction as a single probability value
+  return(list(prediction = mean_prediction))
+  
 }
 
 #* @plumber

### 2024-04-19 paper/paper.qmd
Rename paper (2).qmd to paper.qmd

@@
 library(lintr)
-
 library(lme4)
@@
 
-The analysis reveals age, wealth, and education level have a positive relationship with voting liberal, while children number, gender, and province do not.
+The statistical analysis indicates that demographic factors such as age, gender, education, family size, and regional differences significantly influence voter preferences towards the Liberal Party.
+Older age groups and individuals with higher educational qualifications are more likely to support the Liberals, while males and larger families tend to show lower support.
+Regional variability also plays a crucial role, highlighting the diverse political landscapes across provinces.
+Understanding these factors is essential for several reasons.
+It allows political strategists to craft targeted campaign messages and policies that resonate with specific demographic groups, potentially swaying voter decisions.
+Additionally, this analysis aids in predicting election outcomes and can serve as a valuable tool for academic and governmental studies aiming to understand and address the diverse needs and concerns of the population.
+This insight is critical for fostering a more engaged and informed electorate, leading to more representative governance.
 
@@
 
->**children_number**: the number of children within the family, which includes only six levels (0,1,2,3,4 and 4+ children)
+- **children_number**: the number of children within the family, which includes only six levels (0,1,2,3,4 and 4+ children)
 
@@
 ```
-@fig-percent shows the proportion of the population within each subcategory to the population of the entire category after categorizing all voters according to six different demographic categories.
-
-The demographic data indicates that the majority of the population falls within the age range of 60 to 74 years, accounting for approximately 30% of the sample.
-
-Regarding family structure, 40% of individuals do not have children, which includes those who are unmarried, while a two-child family configuration is the next most prevalent, representing 30% of the sample.
-
-In terms of educational attainment, the predominant qualification is a bachelor's degree. High school graduates and individuals without a university degree each make up about 20% of the population.
-
-As for household income, the distribution appears relatively uniform across different brackets, with a notable concentration of individuals earning between 50k to 75k and those earning more than 125k, both groups constituting about 20%.
-
-The gender composition of the population is slightly skewed towards women, who make up just over 50%, while men represent a marginally lower proportion, just above 40%.
-
-Geographically, a significant portion of the electorate, around 50%, resides in Ontario, reflecting a centralization of voters in this province.
+@fig-percent shows the proportion of the population within each subcategory to the population
+of the entire category after categorizing all voters according to six different demographic categories.
+It reveals that the most populous age segment is 60 to 74 years, comprising roughly
+30% of the sample. The 30-44 and 45-59 age groups each make up about 22% of the electorate,
+forming the backbone of the voters. The number of elderly voters aged 75 and above is the
+smallest. Family structures show that 40% of the cohort is childless, which includes unmarried
+individuals, with two-child families being the second most common at 30%.Voters with four
+or more children represent the lowest percentage of the electorate, with their combined share
+possibly only around 5%. Educationally, bachelor’s degrees prevail as the highest attainment
+for approximately 20% of people, closely followed by high school graduates and non-university
+educated individuals. Income distribution is fairly even across the spectrum, yet there’s a
+discernible cluster of earners between $50k to $75k and above $125k, each group accounting
+for 20% of the population. The gender mix leans slightly towards women, who exceed 50%,
+with men forming just over 40%. Geographically, half of the voters are centralized in Ontario,
+signifying a voter concentration in that province.
 
@@
 ```
-@fig-vote-percent displays the probability of voters voting for three main parties (the Liberal, the Conservative and the NDP) within each subcategory (e.g.
-'18-29') under six different demographic categories (e.g.
-'age'), after classifying all voters according to these demographic categories.
+@fig-vote-percent displays the probability of voters voting for three main parties (the Liberal, the Conservative
+and the NDP) within each subcategory (e.g. ‘18-29’) under six different demographic
+categories (e.g. ‘age’), after classifying all voters according to these demographic categories.
+There appears to be a positive correlation between age and the percentage of votes for the Liberal party. As voters age, support for the Liberal party appears to steadily rise from about
+50% among young people aged 18-29 to just over 50% among those over 75. However, this is
+slightly less than the support rate for the Conservative party among people aged 45 and older.
+Conversely, the NDP sees the opposite trend, with younger voters showing higher support
+rates.
+From the lowest to the highest education levels, support for the Liberal party shows a relatively
+stable trend with a slight increase. Those with a bachelor’s degree appear to be the most
+steadfast in their support for the Liberals, with a support rate above 40%.Among voters with
+education levels lower than a university certificate, the Conservative party is more popular
+than the Liberal party.
 
-Age: There appears to be a positive correlation between age and the percentage of votes for the Liberal party.
-As voters age, from the young demographic of 18-29 to those over 75, support for the Liberals seems to steadily rise from about 50% to just over 50%.
-
-Education Level: From the lowest to the highest education levels, support for the Liberal party shows a relatively stable trend with a slight increase.
-Those with a bachelor's degree appear to be the most steadfast in their support for the Liberals, with a support rate above 40%.
-
-Gender: Female voters show higher support for the Liberal party than males, indicating that gender may be a significant factor in support for the Liberals.
-
-Number of Children: Families with more children seem to be more inclined to support the Liberal party, especially when there are four or more children, where the support rate peaks at about 45%.
-
-Family Income: The Liberal party enjoys higher support in the middle-income brackets, while there is a decline in support among the higher income bracket (over 125k).
-
-Province: Support for the Liberals is significantly higher in Ontario (ON) than in other provinces, possibly indicating the impact of regional factors on support for the Liberal party.
+Male voters show higher support for the Liberal party than females, but they also tend to favor
+the Conservative party more. Female support for the three parties is almost identical. Voters
+with one and four children show the highest support for the Liberal party, with 40% of them
+voting Liberal. Support for the Liberal party among voters with other numbers of children is
+fairly consistent, remaining around 35%. In families with multiple children, support for the
+Conservative party significantly increases, surpassing that for the Liberal party. In terms of
+income, the Liberal party has higher support among the middle-income class, with a general
+trend consistent with the Conservative party. However, support decreases in the higher income
+bracket ($100,000 to $125,000), slightly below the Conservative party.
+Ontario, the most populous province, shows a slightly higher support rate for the Liberal party
+compared to the average support in other provinces, just over 40%, and is slightly ahead of the
+other two parties. New Brunswick has the highest support rate for the Liberals, with over half
+of the population voting for the Liberal party. Saskatchewan shows the least support for the
+Liberals, with only about 20% of the vote. In contrast, the vote shares for the Conservative and
+Liberal parties in these two provinces are clearly polarized and significantly different. Overall,
+there is a clear preference for the three parties across different provinces, with swing regions
+being few.
 
@@
 ## Multilevel Logistic Regression Model
-
-\begin{align}
-y_i | \pi_i &\sim \text{Bern}(\pi_i) \\
-\text{logit}(\pi_i) &= \beta_0 + \alpha_{a[i]}^{\text{age}}+ \alpha_{g[i]}^{\text{gender}} + \alpha_{e[i]}^{\text{education level}} 
-+\alpha_{f[i]}^{\text{family income}} + \alpha_{c[i]}^{\text{children number}} + \alpha_{s[i]}^{\text{state}} \\
-\beta_0 &\sim \text{Normal}(0, 2.5) \\
-\alpha_{a}^{\text{age}} &\sim \text{Normal}(0, 2.5) \text{ for } g = 1,2,3,4,5 \\
-\alpha_{g}^{\text{gender}} &\sim \text{Normal}(0, 2.5) \text{ for } g = 1,2 \\
-\alpha_{e}^{\text{education level}} &\sim \text{Normal}(0, 2.5) \text{ for } g = 1,2,3,4,5,6 \\
-\alpha_{f}^{\text{family income}} &\sim \text{Normal}(0, 2.5) \text{ for } g = 1,2,3,4,5,6 \\
-\alpha_{c}^{\text{children number}} &\sim \text{Normal}(0, 2.5) \text{ for } g = 1,2,...,6 \\
-\alpha_{s}^{\text{state}} &\sim \text{Normal}(0, \sigma_{\text{state}}^2) \text{ for } s = 1,2,...,9 \\
-\sigma_{\text{state}} &\sim \text{Exponential}(1)
-\end{align}
 
@@
 ```{r}
+#| label: tbl-liberal-3
+#| tbl-cap: Coefficients of Liberal Party Model In Different Province
+#| warning: false
+#| echo: false
+#Coefficient table of model_liberal
+a = coef(liberal_model)
+b <- a$province 
+b%>%
+select(c(1:1))%>%
+kable()
+
+```
+@tbl-liberal-3 shows the intercept for each province. The coefficients align with the trend illustrated in @fig-vote-percent.
+
+```{r}
 #| label: fig-liberal
@@
 However, since the interval does not include zero, it suggests that there is likely a significant impact, but the exact magnitude of this effect is less certain.
-
-```{r}
-#| label: tbl-liberal-3
-#| tbl-cap: Coefficients of Liberal Party Model In Different Province
-#| warning: false
-#| echo: false
-#Coefficient table of model_liberal
-a = coef(liberal_model)
-b <- a$province 
-b%>%
-select(c(1:1))%>%
-kable()
-
-```
-@tbl-liberal-3 shows the intercept for each province. The coefficients align with the trend illustrated in @fig-vote-percent.
 

### 2024-04-19 paper/paper.qmd
Update paper.qmd

@@
   - Yichen ji
-thanks: "Code and data are available at: https://github.com/Selinayichenji/Canadian_election_prediction.git."
+thanks: "Code and data are available at: https://github.com/Selinayichenji/CES2021_Liberal_Analysis-.git."
 date: today

### 2024-04-19 paper/paper.qmd
Update paper.qmd

@@
 
-Besides the programming tool, we also employ the following packages: `here`[@here], `ggplot2`[@gg2], `dplyr` [@dp], `tidyverse` [@td], `tidyr`[@tdr], `kableExtra`[@kbe], `arrow`[@ar] and `lintr`[@ltr].
+Besides the programming tool, we also employ the following packages: `here`[@here], `ggplot2`[@gg2], `dplyr` [@dp], `tidyverse` [@td], `tidyr`[@tdr], `kableExtra`[@kbe], `arrow`[@ar], `lintr`[@ltr] and `lme4`[@lme4].
 
@@
 
-- **Age**:five age groups: 18-29 years old, 30-44 years old, 45-59 years old, 60-74 years old, and above 74 years old.
+- **Age**: five age groups: 18-29 years old, 30-44 years old, 45-59 years old, 60-74 years old, and above 74 years old.
 

### 2024-04-19 paper/paper.qmd
Update paper.qmd

@@
 ---
-title: "Analyzing how sociodemographic characteristics influence voting for the Liberal Party of Canada"
+title: "Older, Wealthier, and More Educated: The Profile of Canadians More Likely to Vote Liberal"
 subtitle: "Decoding CES 2021 Vote Data by using A Multilevel Logistic Regression Model"
